### 2023-03-31 manuscript.tex
update data availability [ci skip]
This build is based on
https://github.com/MMV-Lab/im2im-paper/commit/7aec32e213021f4411b07c4ae3ddb6abc7fba11c.

This commit was created by the following CI build and job:
https://github.com/MMV-Lab/im2im-paper/commit/7aec32e213021f4411b07c4ae3ddb6abc7fba11c/checks
https://github.com/MMV-Lab/im2im-paper/actions/runs/4571207976

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/ed68e62ce4e8fd69a528319870ab7e5ce2c2abc8/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/ed68e62ce4e8fd69a528319870ab7e5ce2c2abc8}{MMV-Lab/im2im-paper@ed68e62}
on March 30, 2023.

@@

All data used in this work were from public repositories, released with other publications. The scripts we used to download and re-organize the data can be found in our release repository: https://github.com/MMV-Lab/mmv\_im2im/tree/main/paper\_configs/prepare\_data

>>>>

This manuscript
(\href{https://MMV-Lab.github.io/im2im-paper/v/7aec32e213021f4411b07c4ae3ddb6abc7fba11c/}{permalink})
was automatically generated
from \href{https://github.com/MMV-Lab/im2im-paper/tree/7aec32e213021f4411b07c4ae3ddb6abc7fba11c}{MMV-Lab/im2im-paper@7aec32e}
on March 31, 2023.

@@

All data used in this work were from open-accessible public repositories, released with other publications under open-source licenses. The scripts we used to download and re-organize the data can be found in our release repository: https://github.com/MMV-Lab/mmv\_im2im/tree/main/paper\_configs/prepare\_data
